R-LIME: Rectangular Constraints and Optimization for Local Interpretable Model-agnostic Explanation Methods

### 2024-02-13 paper.tex
Remove errors by linter

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%

@@

\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%

\usepackage{amssymb} % for \mathbb
\usepackage{cleveref} % for \cref
\usepackage{bbm} % for \mathbbm
\usepackage{booktabs} % for \toprule, \midrule, \bottomrule
\usepackage{pgffor} % for \foreach
\usepackage{csvsimple} % for \csvreader
\usepackage{array} % for m column type

% Fig. 1a -> Fig. 1(a)
\usepackage[labelformat=simple]{subcaption}
\graphicspath{{./data/}{./python/data/}}
\renewcommand\thesubfigure{(\alph{subfigure})}
\makeatletter
\def\caption@documentclass{elsarticle}%
\makeatother

\usepackage{algorithm}
\usepackage{algpseudocode}

\input{macro}

\begin{document}
%
\title{%
  R-LIME: Rectangular Constraints and Optimization for Local Interpretable
  Model-agnostic Explanation Methods}
%
\titlerunning{%
  R-LIME: Rectangular Constraints and Optimization for LIME Methods
}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Genji Ohara\inst{1}\orcidID{0009-0000-5854-2820} \and
  Keigo Kimura\inst{1}\orcidID{0000-0002-3614-6568} \and
  Mineichi Kudo\inst{1}\orcidID{0000-0003-1013-3870}
}
%
\authorrunning{G. Ohara et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Division of Computer Science and Information Technology\\
  Graduate School of Information Sci.\ and Tech.,
  Hokkaido University\\
  Sapporo 060-0814, JAPAN,\\
  \email{\{genji-ohara, kimura5, mine\}@ist.hokudai.ac.jp}}

\maketitle              % typeset the header of the contribution
%
% The abstract should briefly summarize the contents of the paper in
% 150--250 words.

\begin{abstract}
  In recent years, complex machine learning models such as deep neural networks
  have been used in various industrial fields due to their high accuracy.
  However, its complexity has been a major obstacle to implementation
  in decision-making situations where transparency of the decision process is required.
  In order to solve this problem,
  various post-hoc explanation methods have been proposed,
  but they have not been able to achieve interpretability of
  both the explanation and its scope.
  We propose a new method that interprets complex models in an interpretable
  approximation region.
  R-LIME locally approximizes a complex decision boundary with a linear classifier
  and maximizes the approximation region as long as the accuracy of the linear
  model is higher than a specified threshold.
  We demonstrate the effectiveness of the proposed method through a qualitative
  and quantitative evaluation using a real-world dataset.
  Finally, we discuss limitations and future work of the proposed method.
  % 148 words
  \keywords{Interpretable machine learning \and Local surrogate model}
\end{abstract}

@@

Existing studies on post hoc explanations categorize into model-dependent and
model-agnostic methods,
depending on their dependence on the model's structure.
Model-dependent methods primarily focus on deep neural networks and
explain the model's behavior using internal parameters.
While they allow a direct approach to the model, 
applying the same method to models with different structures is often challenging. On the other hand, model-agnostic methods do not rely on internal parameters and utilize only the model's output. Although they provide high generality, their information is constrained, making them more versatile. Model-agnostic methods further classify into global and local methods based on their treatment of input space. Global methods aim to explain the model's behavior across the entire input space, seeking explanations valid for any input. However, providing global explanations becomes challenging as the model's complexity increases. Local methods, in contrast, explain the model's output for a specific input (focus point) in the vicinity of that input. While local methods offer simple and accurate explanations compared to global methods, their applicability is limited.

@@

To address the limitations of LIME,
we propose an algorithm that interprets complex models
in an interpretable approximation region,
taking inspiration from another explanation method called Anchor
\cite{ribeiro2018anchors}.
Our proposed method maximizes the accuracy of the learned approximation model
within a rectangular approximation region under lower-bound constraints.
The resulting rectangular region is expressed as a conjunction of predicates
related to features, enhancing interpretability for the user.

@@

\subsection{Anchor \cite{ribeiro2018anchors}}\label{sec:anchor}
Anchor represents a rectangular region, expressed as a conjunction of predicates (rules) related to features, that maximizes the probability of the black-box classifier $f$ outputting $f(x)$ within the region. It aims to highlight important features contributing significantly to the output (\cref{fig:anchor}).

For a discrete $m$-dimensional input space $\ispace$ with a trained black-box classifier $f: \ispace \to \{0,1\}$, an instance $x \in \ispace$, and a distribution $\mathcal{D}$ over the input space, a rule $A(z) = a_{i_1}(z) \wedge a_{i_2}(z) \wedge \dots \wedge a_{i_t}(z)$ is defined. The predicates $a_i(z)$ evaluate to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise. The precision $\Prec(A)$ and coverage $\Cov(A)$ of the rule $A$ are defined as follows:
\begin{align}
  \Prec(A) & =\mathbb{E}_{z\sim\mathcal{D}(z|A)}
  [\mathbbm{1}_{f(z)=f(x)}], \label{eq:anchor_def_prec} \\
  \Cov(A)  & =\mathbb{E}_{z\sim\mathcal{D}(z)}[A(z)].
\end{align}

Here, $\mathcal{D}(z|A)$ is the conditional distribution in the region where the rule $A$ is true.
% When sampling the perturbation vector $z$ according to the distribution $\mathcal{D}$,
$\Prec(A)$ represents the probability that the output of $f$ matches between the perturbation $z$ and the focal point $x$ in the region $A$, and $\Cov(A)$ expresses the probability that the perturbation $z$ fits into $A$.

An Anchor maximizes coverage within the given threshold $\tau$ while maintaining precision.
However, direct computation of \cref{eq:anchor_def_prec} is not feasible, and it is evaluated using PAC (Probably Approximately Correct) through sampling.
Introducing a confidence level $1-\delta$ $(0\le\delta\le1)$, the precision constraint is relaxed as follows:
\begin{equation}
  \label{eq:const_prec}
  P(\Prec(A)\ge\tau)\ge1-\delta.
\end{equation}
Thus, the following optimization problem is solved:
\begin{equation}
  \label{eq:main_problem}
  A^*=\underset{A \text{ s.t. } P(\Prec(A)\ge\tau)\ge1-\delta\wedge A(x)=1}
  {\arg\max}\Cov(A).
\end{equation}

@@

\section{Proposed Method}
\begin{figure}[tb]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{lime}
    \caption{%
      LIME: Locally approximates decision boundaries around the focal point.}\label{fig:lime}
  \end{subfigure}%
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{anchor}
    \caption{Anchor: Maximizes coverage of a rectangular region containing the focal point under precision constraints.}\label{fig:anchor}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=0.85\textwidth]{bella}
    \caption{%
      BELLA: Explores a subset of the dataset, maximizing similarity between the local linear approximation model and the black-box classifier.}\label{fig:bella}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{rlime3}
    \caption{%
      R-LIME: Maximizes coverage of a rectangular region containing the focal point under lower constraints on the accuracy of the approximation model.}\label{fig:rlime}
  \end{subfigure}
  \caption{%
    Visual comparison of LIME, Anchor, BELLA and R-LIME (our proposed method).
    The solid line represents the rectangular region containing the focal
    point, and the dashed line represents the learned approximation model.
  }
\end{figure}

\subsection{Overview}
The proposed method aims to overcome the limitations of LIME \cite{ribeiro2016why} and its improvement methods such as Anchor \cite{ribeiro2018anchors} and BELLA \cite{radulovic2023bella}. Similar to LIME, the proposed method locally approximates the given black-box classifier $f$ around the focal point $x$ using a linear model $g$. However, by adopting a rectangular perturbation region similar to Anchor, it represents predicates (rules) concerning features. The accuracy of explanations is defined as the "accuracy" of rules, and the "coverage" of rules defines the generality of explanations. The proposed method maximizes coverage under lower constraints on accuracy (\cref{fig:rlime}).

Anchor maximizes the coverage of region $A$ within which the output of the black-box classifier $f$ matches $f(x)$ with respect to the probability under lower constraints. The proposed method, on the other hand, learns an approximation model $g$ within the rectangular region $A$ and maximizes the coverage of $A$ under lower constraints on the accuracy of $g$. We modify the definition of accuracy using \cref{eq:anchor_def_prec} as follows:
\begin{equation}
  \Prec(A)=\underset{g\in G}{\max}\ \mathbb{E}_{z\sim\mathcal{D}(z|A)}
  [\mathbbm{1}_{f(z)=g(z)}]. \label{eq:def_prec}
\end{equation}
Here, $G$ represents the set of possible linear approximation models. By solving the optimization problem in \cref{eq:main_problem} under this modified accuracy definition, we can select rules that learn high-accuracy approximation models, among which the coverage is maximized. The proposed method's algorithm, shown in \cref{sec:alg}, is largely based on the algorithms used in Anchor.

@@

\subsection{Algorithm}\label{sec:alg}
{%
  \begin{figure}[t]
    \centering
    \includegraphics[width=0.32\textwidth]{rlime1}
    \includegraphics[width=0.32\textwidth]{rlime2}
    \includegraphics[width=0.32\textwidth]{rlime3}
    \caption[Overview of the R-LIME Algorithm]{%
      Overview of the R-LIME algorithm. The progression of the algorithm from left to right is illustrated. The solid red line represents the rectangular region $A$, and the red dashed line represents the linear approximation model $g$ learned within $A$. The initial value of $A$ is an empty rule (entire input space), and predicates are added to $A$, reducing coverage. The process continues until $\Prec(A)\ge\tau$, at which point the rule with the maximum coverage is output.
    }
  \end{figure}
  \begin{algorithm}[p]
    \input{alg1}
  \end{algorithm}
  \begin{algorithm}[p]
    \input{alg2}
  \end{algorithm}
  \def\myidt{\hspace{\algorithmicindent}}
  \begin{algorithm}[p]
    \input{alg3}
  \end{algorithm}
  \begin{algorithm}[p]
    \input{alg4}
  \end{algorithm}
}
For non-convex optimization problems like \cref{eq:main_problem}, greedy methods are often employed. However, greedy methods tend to converge to local optima, and to address this, the proposed method utilizes beam search, which selects multiple candidates at each iteration. The pseudocode is shown in \cref{alg:greedy_search}.

\subsubsection{Candidate Rule Generation}
To generate new candidate rules, one additional predicate is added to each of the $B$ candidate rules obtained in the previous iteration. The pseudocode is shown in \cref{alg:generate_cands}. Here, $T(x)$ represents the set of attribute-value pairs (predicates) that $x$ possesses, and $T(x)\setminus A$ represents the conjunction of predicates in $T(x)$ not included in rule $A$.

@@

\subsubsection{Selection of Rule with Maximum Coverage Meeting Constraints}
To meet the constraint in \cref{eq:const_prec}, rule $A$ must satisfy the lower constraint
\begin{equation}
  \label{eq:stop_condition}
  \Prec_{l}(A,\delta)>\tau
\end{equation}
where $\Prec_{l}(A,\delta)$ is the lower bound on accuracy and $\delta$ is a small positive value. To check this condition, the algorithm performs a binary search on $\delta$ to find the smallest $\delta$ that satisfies \cref{eq:stop_condition}. The pseudocode is shown in \cref{alg:largest_valid_cand}.
\newline

@@

\subsection{Qualitative Evaluation}
\subsubsection{Experimental Setup}\label{sec:exp_setting}
{%
  \renewcommand{\arraystretch}{1.05}
  \begin{table}[tbp]
    \centering
    \caption[Attributes and overview of the recidivism dataset used in the experiments]{%
      Attributes and overview of the recidivism dataset used in the experiments. Continuous features are discretized, and only binary and ordinal features are considered.
    }\label{tab:rcdv}
    \begin{tabular}{llc}
      \toprule
      Attribute              & Overview                              & \# of Possible Values \\
      \midrule
      Race                   & Race (Black or White)                 & 2                     \\
      Alcohol                & Presence of serious alcohol issues    & 2                     \\
      Junky                  & Drug usage                            & 2                     \\
      Supervised Release     & Supervised release                    & 2                     \\
      Married                & Marital status                        & 2                     \\
      Felony                 & Felony or not                         & 2                     \\
      WorkRelease            & Participation in work release program & 2                     \\
      Crime against Property & Crime against property or not         & 2                     \\
      Crime against Person   & Crime against a person or not         & 2                     \\
      Gender                 & Gender (Female or Male)               & 2                     \\
      Priors                 & Number of prior offenses              & 4                     \\
      YearsSchool            & Years of formal education completed   & 4                     \\
      PrisonViolations       & Number of prison rule violations      & 3                     \\
      Age                    & Age                                   & 4                     \\
      MonthsServed           & Months served in prison               & 4                     \\
      \midrule
      Recidivism             & Recidivism or not                     & 2                     \\
      \bottomrule
    \end{tabular}
  \end{table}
}

@@

  {%
    \def\vval{0pt}
    \def\dir{python/exp1}
    \def\Asample{0012}
    \def\Bsample{0011}
    \def\AB#1{\ifnum#1=0 A\else B\fi}

    % \def\rcdvIdx#1{\ifnum#1=0 0253\else 0599\fi}
    \def\index#1{\ifnum#1=0 \Asample \else \Bsample \fi}

>>>>

@@

\documentclass[runningheads]{llncs}

% If possible, figure files should be included in EPS format.

% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}

% The following code is used to remove the warning with subcaption package:
% ------------------------------
% Package caption Warning: Unknown document class (or package),
% standard defaults will be used.
% ------------------------------
% cf. https://teratail.com/questions/q2vuwf6skm5hph
\makeatletter
\def\caption@documentclass{elsarticle}
\makeatother

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amssymb} % for \mathbb
\usepackage{array} % for m column type
\usepackage{bbm} % for \mathbbm
\usepackage{booktabs} % for \toprule, \midrule, \bottomrule
\usepackage{cleveref} % for \cref
\usepackage{csvsimple} % for \csvreader
\usepackage[T1]{fontenc} % for T1 font encoding
\usepackage{graphicx} % for \includegraphics
\usepackage{pgffor} % for \foreach
\usepackage[labelformat=simple]{subcaption} % for subfigure environment

% The following code is used to remove the warning with bibliography:
% ------------------------------
% Underfull \hbox (badness 2653) in paragraph at lines 28--34
% ------------------------------
% cf. https://tex.stackexchange.com/questions/10924/underfull-hbox-in-bibliography
\apptocmd{\sloppy}{\hbadness 10000\relax}{}{}

% set the path for figures
\graphicspath{{./data/}{./python/data/}}

% set the label format for subcaption
\renewcommand\thesubfigure{(\alph{subfigure})}

% settings for cleveref
\crefname{figure}{Fig.}{Figs.}
\crefname{table}{Tab.}{Tabs.}

% import the TeX file containing macro definitions
\input{macro}

\begin{document}

% Authentic title
\title{%
  R-LIME: Rectangular Constraints and Optimization for Local Interpretable
  Model-agnostic Explanation Methods}

% Abbreviated title for the running head
\titlerunning{%
  R-LIME: Rectangular Constraints and Optimization for LIME Methods
}

% Author names and ORCID IDs
\author{Genji Ohara\inst{1}\orcidID{0009-0000-5854-2820} \and
  Keigo Kimura\inst{1}\orcidID{0000-0002-3614-6568} \and
  Mineichi Kudo\inst{1}\orcidID{0000-0003-1013-3870}
}

% Abbreviated author list for the running head (First names are abbreviated)
% If there are more than two authors, 'et al.' is used.
\authorrunning{G. Ohara et al.}

% The authors' affiliations
\institute{Division of Computer Science and Information Technology\\
  Graduate School of Information Sci.\ and Tech.,
  Hokkaido University\\
  Sapporo 060-0814, JAPAN,\\
  \email{\{genji-ohara, kimura5, mine\}@ist.hokudai.ac.jp}}

% typeset the header of the contribution
\maketitle              %

% The abstract should briefly summarize the contents of the paper in
% 150--250 words.
\begin{abstract}
  In recent years, complex machine learning models such as deep neural networks
  have been used in various industrial fields due to their high accuracy.
  However, its complexity has been a major obstacle to implementation
  in decision-making situations where transparency of the decision process is required.
  In order to address this problem,
  various post-hoc explanation methods have been proposed,
  but they have not been able to achieve interpretability of
  both the explanation and its scope.
  We propose a new method, R-LIME,
  which interprets complex classifiers in an interpretable scope.
  R-LIME locally approximizes a complex decision boundary linearly
  in a rectangular region
  and maximizes the region as long as the accuracy of the linear
  classifier is higher than a specified threshold.
  The resulting rectangular region is interpretable for users because it is
  expressed as a conjunction of feature predicates.
  We demonstrate the effectiveness of the proposed method through qualitative
  and quantitative experiments using a real-world dataset.
  Finally, we discuss limitations and future work of the proposed method.
  % 148 words
  \keywords{Interpretable machine learning \and Local surrogate model}
\end{abstract}

@@

Existing methods on post hoc explanations categorize into model-dependent and
model-agnostic methods,
based on their dependence on the model's structure.
Model-dependent methods primarily focus on deep neural networks and
explain the models' behavior using their parameters.
While they allow a direct approach to the model,
applying the same method to models with different structures is often challenging.
On the other hand,
model-agnostic methods do not rely on the models' parameters and utilize only their output.
Although they are applicable to any model, available information is limited.
Model-agnostic methods further classify into global and local methods
based on their treatment of input space.
Global methods aim to explain the model's behavior across the entire input space,
seeking explanations valid for any input.
However, providing global explanations becomes challenging as the model's complexity increases.
Local methods, in contrast, explain the model's output for a specific input
(focus point) in the vicinity of that input.
While local methods offer more simple and accurate explanations than global methods,
the scope of the explanation is limited to the vicinity of the focus point.

@@

To address the limitations of LIME,
we propose an algorithm that interprets complex models
in an interpretable approximation region,
taking inspiration from another explanation method called Anchor
\cite{ribeiro2018anchors}.
Our proposed method maximizes the accuracy of the learned approximation model
within a rectangular approximation region under lower-bound constraints.
The resulting rectangular region is expressed as a conjunction of feature predicates,
enhancing interpretability for the user.

@@

\subsection{Anchor \cite{ribeiro2018anchors}}\label{sec:anchor}
Anchor represents a rectangular region,
expressed as a conjunction of feature predicates (rules),
that maximizes the probability of the black-box classifier $f$ outputting $f(x)$ within the region. It aims to highlight important features contributing significantly to the output (\cref{fig:anchor}).

For a discrete $m$-dimensional input space $\ispace$ with a trained black-box classifier $f: \ispace \to \{0,1\}$, an instance $x \in \ispace$, and a distribution $\mathcal{D}$ over the input space, a rule $A(z) = a_{i_1}(z) \wedge a_{i_2}(z) \wedge \dots \wedge a_{i_t}(z)$ is defined.
The predicates $a_i(z)$ evaluate to true ($=1$) when $z_i = x_i$ and false ($=0$) otherwise.
The accuracy $\Prec(A)$ and coverage $\Cov(A)$ of the rule $A$ are defined as follows:
\begin{align}
  \Prec(A) & =\mathbb{E}_{z\sim\mathcal{D}(z|A)}
  [\mathbbm{1}_{f(z)=f(x)}], \label{eq:anchor_def_prec} \\
  \Cov(A)  & =\mathbb{E}_{z\sim\mathcal{D}(z)}[A(z)].
\end{align}

where $\mathcal{D}(z|A)$ is the conditional distribution in the region where the rule $A$ is true.
% When sampling the perturbation vector $z$ according to the distribution $\mathcal{D}$,
$\Prec(A)$ represents the probability that the output of $f$ matches between the perturbation $z$ and the focal point $x$ in the region $A$, and $\Cov(A)$ expresses the probability that the perturbation $z$ fits into $A$.

An Anchor maximizes coverage within the given threshold $\tau$ while maintaining accuracy.
However, direct computation of \cref{eq:anchor_def_prec} is not feasible, and it is evaluated using PAC (Probably Approximately Correct) through sampling.
Introducing a confidence level $1-\delta$ $(0\le\delta\le1)$, the accuracy constraint is relaxed as follows:
\begin{equation}
  \label{eq:const_prec}
  P(\Prec(A)\ge\tau)\ge1-\delta.
\end{equation}
Thus, the following optimization problem is solved:
\begin{equation}
  \label{eq:main_problem}
  A^*=\underset{A \text{~s.t. } P(\Prec(A)\ge\tau)\ge1-\delta\wedge A(x)=1}
  {\arg\max}\Cov(A).
\end{equation}

@@

\section{Proposed Method}
\begin{figure}[tb]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{lime}
    \caption{%
      LIME: Locally approximates the decision boundary around the focal point.}\label{fig:lime}
  \end{subfigure}%
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{anchor}
    \caption{Anchor: Maximizes coverage of a rectangular region containing the focal point under accuracy constraints.}\label{fig:anchor}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=0.85\textwidth]{bella}
    \caption{%
      BELLA: Explores a subset of the dataset, maximizing similarity between the local linear approximation model and the black-box classifier.}\label{fig:bella}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{rlime3}
    \caption{%
      R-LIME: Maximizes coverage of a rectangular region containing the focal point under lower constraints on the accuracy of the approximation model.}\label{fig:rlime}
  \end{subfigure}
  \caption{%
    Visual comparison of LIME, Anchor, BELLA and R-LIME (our proposed method).
    The solid line represents the rectangular region containing the focal
    point, and the dashed line represents the learned approximation model.
  }
\end{figure}

\subsection{Overview}
We propose R-LIME,
a method that aims to address the limitations of LIME \cite{ribeiro2016why}
and its improvement methods such as
Anchor \cite{ribeiro2018anchors} and BELLA \cite{radulovic2023bella}.
Similar to LIME,
the proposed method locally approximates the given black-box classifier $f$
around the focal point $x$ by a linear model $g$.
However,
by adopting a rectangular perturbation region similar to Anchor,
it represents feature predicates (rules).
The accuracy of explanations is defined as the "accuracy" of rules,
and the "coverage" of rules defines the generality of explanations.
The proposed method maximizes coverage under lower constraints on accuracy
(\cref{fig:rlime}).

Anchor maximizes the coverage of region $A$ within which the output of the black-box classifier $f$ matches $f(x)$ with respect to the probability under lower constraints. The proposed method, on the other hand, learns an approximation model $g$ within the rectangular region $A$ and maximizes the coverage of $A$ under lower constraints on the accuracy of $g$. We modify the definition of accuracy using \cref{eq:anchor_def_prec} as follows:
\begin{equation}
  \Prec(A)=\underset{g\in G}{\max}\ \mathbb{E}_{z\sim\mathcal{D}(z|A)}
  [\mathbbm{1}_{f(z)=g(z)}]. \label{eq:def_prec}
\end{equation}
where $G$ represents the set of possible linear approximation models. By solving the optimization problem in \cref{eq:main_problem} under this modified accuracy definition, we can select rules that learn high-accuracy approximation models, among which the coverage is maximized. The proposed method's algorithm, shown in \cref{sec:alg}, is largely based on the algorithms used in Anchor.

@@

\subsection{Algorithm}\label{sec:alg}
{%
  \begin{figure}[t]
    \centering
    \includegraphics[width=0.32\textwidth]{rlime1}
    \includegraphics[width=0.32\textwidth]{rlime2}
    \includegraphics[width=0.32\textwidth]{rlime3}
    \caption{%
      Overview of the R-LIME algorithm.
      The progression of the algorithm from left to right is illustrated.
      The solid line represents the rectangular region $A$,
      and the dashed line represents the linear approximation model $g$
      learned within $A$.
      The initial value of $A$ is an empty rule (entire input space),
      and predicates are added to $A$, reducing coverage.
      The process continues until $\Prec(A)\ge\tau$,
      at which point the rule with the maximum coverage is output.
    }
  \end{figure}
  \begin{algorithm}[p]
    \input{alg1}
  \end{algorithm}
  \begin{algorithm}[p]
    \input{alg2}
  \end{algorithm}
  \def\myidt{\hspace{\algorithmicindent}}
  \begin{algorithm}[p]
    \input{alg3}
  \end{algorithm}
  \begin{algorithm}[p]
    \input{alg4}
  \end{algorithm}
}
For non-convex optimization problems like \cref{eq:main_problem}, greedy methods are often employed. However, greedy methods tend to converge to local optima, and to address this, the proposed method utilizes beam search, which selects multiple candidates at each iteration. The pseudocode is shown in \cref{alg:greedy_search}.

\subsubsection{Candidate Rule Generation}
To generate new candidate rules, one additional predicate is added to each of the $B$ candidate rules obtained in the previous iteration. The pseudocode is shown in \cref{alg:generate_cands}. $T(x)$ represents the set of attribute-value pairs (predicates) that $x$ possesses, and $T(x)\setminus A$ represents the conjunction of predicates in $T(x)$ not included in rule $A$.

@@

\subsubsection{Selection of the Rule with Maximum Coverage Meeting the Constraint}
To satisfy the constraint imposed by \cref{eq:const_prec}, rule $A$ needs to fulfill the lower bound constraint:
\begin{equation}
  \Prec_{l}(A,\delta)>\tau
  \label{eq:stop_condition}
\end{equation}
where $\Prec_{l}(A,\delta)$ represents the lower limit of the $100(1-\delta)$\% confidence interval for $\Prec(A)$.
If the received set of candidate rules, $\mathcal{A}$, includes a rule satisfying \cref{eq:stop_condition},
the one with the maximum coverage among them is selected, and the iteration is concluded.
If $\mathcal{A}$ does not contain any rule satisfying \cref{eq:stop_condition}, it returns \textbf{null},
and proceeds to the next iteration.
The pseudocode is presented in \cref{alg:largest_valid_cand}.

@@

\subsection{Qualitative Evaluation}
\subsubsection{Experimental Setup}\label{sec:exp_setting}
{%
  \renewcommand{\arraystretch}{1.05}
  \begin{table}[tbp]
    \centering
    \caption{%
      Attributes of the recidivism dataset used in the experiments.
      Continuous features are all discretized
      and only binary and ordinal features are considered.
    }\label{tab:rcdv}
    \begin{tabular}{llc}
      \toprule
      Attribute              & Overview                              & \# of Possible Values \\
      \midrule
      Race                   & Race (Black or White)                 & 2                     \\
      Alcohol                & Presence of serious alcohol issues    & 2                     \\
      Junky                  & Drug usage                            & 2                     \\
      Supervised Release     & Supervised release                    & 2                     \\
      Married                & Marital status                        & 2                     \\
      Felony                 & Felony or not                         & 2                     \\
      WorkRelease            & Participation in work release program & 2                     \\
      Crime against Property & Crime against property or not         & 2                     \\
      Crime against Person   & Crime against a person or not         & 2                     \\
      Gender                 & Gender (Female or Male)               & 2                     \\
      Priors                 & Number of prior offenses              & 4                     \\
      YearsSchool            & Years of formal education completed   & 4                     \\
      PrisonViolations       & Number of prison rule violations      & 3                     \\
      Age                    & Age                                   & 4                     \\
      MonthsServed           & Months served in prison               & 4                     \\
      \midrule
      Recidivism             & Recidivism or not                     & 2                     \\
      \bottomrule
    \end{tabular}
  \end{table}
}

@@

  {%

    \def\dir{python/exp1}
    \def\Asample{0012}
    \def\Bsample{0011}
    \def\index#1{\ifnum#1=0 \Asample \else \Bsample \fi}

    {%
      \def\AB#1{\ifnum#1=0 A\else B\fi}
      \def\mylabel#1{\ifnum#1=0 \label{fig:A-instance}\else \label{fig:B-instance}\fi}
      \renewcommand{\arraystretch}{1.02}
      \begin{figure}[tbp]
        \foreach\a in {0,1}{%
            \centering
            \begin{subfigure}{\textwidth}
              \centering
              \begin{tabular}{p{14em}m{16em}}
                \toprule
                \csvreader[no head, late after line= \\]{%
                  \dir/\index{\a}.csv
                }{}{%
                \ifnum\thecsvrow=16 \midrule\fi\csvcoli & \csvcolii
                }
                \bottomrule
              \end{tabular}
              \caption{Instance~\AB{\a}}\mylabel{\a}
              \vspace{15pt}
            \end{subfigure}
          }
        \vspace{-15pt}
        \caption{Two instances sampled from recidivism dataset.}\label{fig:instance}
      \end{figure}
    }
    {%
      \def\scale{0.315}
      \def\imgwidth{0.495\textwidth}
      \def\hspacebase{\hspace{-1.5em}}
      \def\vspacebase{\vspace{0.5em}}
      \def\vspacebeforecaption{\vspace{-0.4em}}
      \begin{figure}[p]
        \centering
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase
          \includegraphics[scale=\scale]{\dir/lime-\Asample}
          \vspacebeforecaption
          \caption{LIME}\label{fig:A-lime}
          \vspacebase
        \end{subfigure}
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase
          \hspace{1.0em}
          \includegraphics[scale=\scale]{\dir/newlime-\Asample-70}
          \vspacebeforecaption
          \caption{R-LIME ($\tau=0.70$)}\label{fig:A-rlime-70}
          \vspacebase
        \end{subfigure}
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase
          \includegraphics[scale=\scale]{\dir/newlime-\Asample-80}
          \vspacebeforecaption
          \caption{R-LIME ($\tau=0.80$)}\label{fig:A-rlime-80}
        \end{subfigure}
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase
          \includegraphics[scale=\scale]{\dir/newlime-\Asample-90}
          \vspacebeforecaption
          \caption{R-LIME ($\tau=0.90$)}\label{fig:A-rlime-90}
        \end{subfigure}
        \caption{Explanation for Instance A by LIME and R-LIME.}\label{fig:A}
      \end{figure}
      \begin{figure}[p]
        \centering
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase
          \includegraphics[scale=\scale]{\dir/lime-\Bsample}
          \vspacebeforecaption
          \caption{LIME}\label{fig:B-lime}
          \vspacebase
        \end{subfigure}
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase
          \includegraphics[scale=\scale]{\dir/newlime-\Bsample-70}
          \vspacebeforecaption
          \caption{R-LIME ($\tau=0.70$)}\label{fig:B-rlime-70}
          \vspacebase
        \end{subfigure}
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase
          \includegraphics[scale=\scale]{\dir/newlime-\Bsample-80}
          \vspacebeforecaption
          \caption{R-LIME ($\tau=0.80$)}\label{fig:B-rlime-80}
        \end{subfigure}
        \begin{subfigure}[t]{\imgwidth}
          \hspacebase
          \hspace{0em}
          \includegraphics[scale=\scale]{\dir/newlime-\Bsample-90}
          \vspacebeforecaption
          \caption{R-LIME ($\tau=0.90$)}\label{fig:B-rlime-90}
        \end{subfigure}
        \caption{Explanation for Instance B by LIME and R-LIME}\label{fig:B}
      \end{figure}
    }
  }
\subsubsection{Experimental Results}
The results of the experiment are shown in \cref{fig:A,fig:B}.
The values assigned to each attribute name represent the contribution (weights of the learned linear approximation model) to the output of the black-box classifier, normalized such that the absolute sum is 1.
The figures also highlight the five attributes with the highest absolute contribution.
